Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-08-23 paper.Rmd
Continue to write the paper draft

To compare different methods for constructing continuous LoA, smooth curve data were simulated across a range of common biomechanical signals and error characteristics.

The curves were modeled as Fourier series from additively superimposed sine functions. Each data set contains n.strides = 10 curves from n.subj = 11 fictitious test subjects. Each curve consists of t = 101 data points. Note that the curves do not necessarily correspond to real-world signals as we were more concerned with illustrating the underlying principle.

@@

* (3) Heteroscedastic error: Heteroscedasticity across the signal length. The example consists of knee moment curves calculated using two different methods (direct and inverse kinematic approach) (Robinson et al., 2014). The curves were recreated using the example code provided in Robinson et al. (2021).

>>>>

To compare different methods for constructing continuous LoA, several sets of smooth curve data were simulated across a range of common biomechanical signals and error characteristics. The quality of the curves is similar, as the paper is primarily developed for a validation context in which the same movement process is analyzed using similar methods (two measurement devices or models). For the same reason, the curves do not necessarily correspond to real-world signals as we were more concerned with illustrating the respective methods and error characterstics.

All curves were modeled as Fourier series from additively superimposed sine functions. Each data set contains n.strides = 10 curves from n.subj = 11 fictitious test subjects. Each curve consists of t = 101 data points.

@@

* (3) Heteroscedastic (non-gaussian, Weibull distributed) error: Heteroscedasticity across the signal length. The example consists of knee moment curves calculated using two different methods (direct and inverse kinematic approach) (Robinson et al., 2014). The curves were recreated using the example code provided in Robinson et al. (2021).
